---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maeFormula

<!-- badges: start -->

<!-- badges: end -->

The goal of maeFormula is to compute the mae value based on two given input lists.

## Installation

You can install the development version of maeFormula from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2022/assignment-b1-and-b2-YuYT98")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(maeFormula)
## basic example code
predicted_list_1 = list(1,2,3)
actual_list_1 = list(4,5,6)
maeFormula(predicted_list_1, actual_list_1)
```

The code above shows how maeFormula function works. It takes two arguments and the type of each argument has to be a list. Also, the length of two input list has to be the same. No NULL or NA values are allowed in two input lists.

